---
title: "Sample report"
subtitle: "You can have a subtitle too"
author: [Simon Knight]
date: "`r Sys.Date()`"
github-repo: sjgknight/rureporting
site: "bookdown::bookdown_site"
book_filename: "Sample_report"
biblio-style: apalike
split_bib: no
nocite: '@*'
bibliography: ["book.bib", "packages.bib"]
link-citations: yes
description: "You can add a description here"
sharing: no
vignette: >
  %\VignetteIndexEntry{Sample_report}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
output:
  rmarkdown::html_document:
    repo: https://github.com/sjgknight/rureporting
    sharing: no
    download: ["pdf", "epub"]
  bookdown::pdf_book:
    includes:
      in_header: "preamble.tex"
      before_body: "before_body.tex"
    book_filename: "sample_report"
    fig_caption: yes
    css: "style.css"
    output_dir: "_book/pdf/"
    keep_tex: true
    latex_engine: xelatex
    titlepage: true
    titlepage-color: 0d41d1
    titlepage-text-color: f5f4f5
    titlepage-rule-color: f5f4f5
    titlepage-rule-height: 1
    language:
      ui:
        chapter_name: "Part "
header-includes:
  - \usepackage{xcolor}
  - \usepackage{titling}
  - \usepackage{pdfpages}
  - \usepackage{fancyhdr}
  - \usepackage{floatrow}
  - \usepackage{caption}
  - \definecolor{bluerich}{RGB}{13,65,209}
  - \usepackage{titling}
  - \pretitle{\begin{center}
  - \floatsetup[figure]{capposition=top}
  - \includegraphics[width=2in,height=2in]{extdata/logo.png}\LARGE\\}
  - \posttitle{\end{center}}
  - \setlength{\headheight}{23pt}
  - \addtolength{\topmargin}{-11pt}
  - \fancyfoot[L]{\footnotesize\textcolor{bluerich}{\textbf{University of My Institution} \\ Centre for Stuff I Do (CSID) \\ Institute for Collaborator Place (ICP) \\ Department }}
  - \fancyfoot[C]{\thepage}
  - \renewcommand{\footrulewidth}{2pt}
  - \fancyhead[L]{\itshape\nouppercase{\rightmark}}
  - \fancyhead[R]{Section \arabic{chapter}}
  - \pagestyle{fancy}
documentclass: book
---

```{r setup}
library(rureporting)
```

# Working with this document

This report was written as a wrapper site to compile a set of outputs, along with their rationale and the overarching narrative. It was written using a tool called *bookdown*, with the aim to make it easier to navigate the materials without getting lost (and to support export to other formats like PDF). 

This document gives a brief overview of the approach and functions. Essentially it:

1. Takes a set of .docx or .pptx documents and converts them to PDF
1. Creates two report versions, a bs4 website with embedded documents, and a compiled PDF that incorporates all the embedded docs.

This means that:

* People can work in word/powerpoint, etc. as usual, so they don't need to learn any new tools
* The documents can remain disaggregated, so they can be worked on separately, and maintained that way, with updates to the compilation drawing on the most recent version
* The documents can be browsed disaggregated, without getting lost in the detail of the individual components



```{r create-bib, include=FALSE}
#, eval=params$bibupdate
# automatically create a bib database for R packages
#knitr::write_bib(.packages(), "packages.bib", tweak = TRUE) 

#extracted references from word docs using https://rintze.zelle.me/ref-extractor/ 

#collection <- "http://127.0.0.1:23119/better-bibtex/export/collection?/2743773/9Q2H88RP.bibtex"
#http://127.0.0.1:23119/better-bibtex/export/collection?/2743773/all_used.bibtex
#download.file(collection,"book.bib")

#curl::curl_download(collection,"book.bib")

```

```{r load-things, include=FALSE}
#bookdown::render_book('index.Rmd', 'all')

xfun::pkg_load2(c("htmltools", "mime"))
```

```{r set-global-knit, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, out.width = "75%", warnings=F, message=F)

#this one is particularly to hide knitting messages that end up when we include the html fragments. I believe adding quiet = TRUE to render may also work 
knitr::opts_knit$set(progress=FALSE, verbose=FALSE)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

## Basic structure 

The basic structure follows the `bookdown` template. Once you've copied the bookdown template, create a 'data' directory, and subdirectories in that for your components. 

I faffed around trying to create a cover page with latex, and ended up just using a Word version and includepdf. 

## Examples of functions

### include_doc 

Include doc will:

1. Check if the file is already a pdf extension. If TRUE, then it'll either embed (bs4) or includepdf (pdf).
1. If FALSE, then convert to PDF, and same. 
1. In the PDF version, it'll take the chunk name and apply it to the included PDF as a label, this allows the cross-referencing to work, for example \@ref(fig:include_doc_example) should link to the next chunk

```{r include_doc_example, fig.cap="Example of embedding a doc"}
# just show it for pdf sample

sampledoc <- system.file("extdata", "sample_doc.pdf", package = "rureporting")

include_doc(sampledoc)

```

### include_frag

Function include_frag will:

1. Convert docx files to markdown
1. Include the markdown as a child document

Mileage may vary depending on complexity of document, etc. (I found it useful for a couple of simple things)

** Note - include_frag chunks must use the `results='asis'` option **

```{r include_frag_example, fig.cap="Frag include example", results='asis'}

samplefrag <- system.file("extdata", "sample_frag.docx", package = "rureporting")

include_frag(samplefrag)

```

## For other inspiration explore

* https://github.com/ismayc/thesisdown_book/
* https://github.com/UTS-CAS/UTS-CAS_thesis_template
* https://masiraji.github.io/monashthesisdown/
* https://cran.r-project.org/web/packages/reporter/index.html
* https://numbats.github.io/monash/
* https://ehyaei.github.io/MPIThemes/articles/articles/01_pdf_report_template_customization.html
* https://ulriklyngs.com/post/2021/12/02/how-to-adapt-any-latex-template-for-use-with-r-markdown-in-four-steps/
* https://cran.r-project.org/web/packages/memoiR/vignettes/memoiR.html


## Things to explore later (or, junk code)

<!--

      in_header: `'r system.file("extdata/preamble.tex", package="mypackage")`'`
      before_body: `'r system.file("extdata/before_body.tex", package="mypackage")`'`
      
      
# I added this param with the idea to create a conditional update of the bibliography...it does not work.
params:
  bibupdate:
    label: "Update bibliography (true to update, false to skip)"
    value: FALSE
    input: radio
    choices: [TRUE,FALSE]

    header:
      includes:
        in_header: "preamble.tex"


`r if (knitr:::is_latex_output()) {

}  # References used {-} `

    knitr::raw_latex()

r if (knitr:::is_html_output())  # References used {-} 



  - \usepackage[style=apa, backend=biber]{biblatex}

  bookdown::pdf_book:
    fig_caption: yes
    base_format: bookdown::pdf_document2
    css: "style.css"
    keep_tex: true
    latex_engine: xelatex
    titlepage: true
    titlepage-color: 0d41d1
    titlepage-text-color: f5f4f5
    titlepage-rule-color: f5f4f5
    titlepage-rule-height: 1
    highlight: tango
    output_dir: "unmerged_book"
    
    -->

<!-- everything below here can be ignored for authors, it just loads some code/sets some options -->

<!-- 
  bookdown::gitbook:
    output_dir: "_book/gitbook"
    lib_dir: assets
    split_by: section
    repo: https://github.com/sjgknight/iyarn
    download: ["pdf", "epub"]
    css: "style.css"
    config:
      toolbar:
        sharing: no



  - \fancyfoot[R]{"Knight, S., Potts, M., Mills, C., Lee, P. (2022). iyarn: Developing the Evidence Base – Final Project Report. University of Technology Sydney."}
  - \newcommand{\helv}{%\fontfamily{phv}\fontseries{b}\fontsize{9}{11}\selectfont}

  - \usepackage[usenames,dvipsnames]{xcolor}
  - \definecolor{bluerich}{rgb}{13,65,209}
  
    - \fancyfoot[L]{\textcolor{bluerich}{\textbf{University of Technology Sydney} \\ Centre for Research on Education in a Digital Society (CREDS) \\ Institute for Public Policy and Governance (IPPG) \\TD School}}

    - \fancyfoot[L]{\textcolor{bluerich}{\textbf}{University of Technology Sydney} \\ Centre for Research on Education in a Digital Society (CREDS) \\ Institute for Public Policy and Governance (IPPG) \\TD School}

  - \newenvironment{headfoot}{\textcolor}{bluerich}
  - \begin{headfoot}
  
    - \let\oldfootrule\fancyfoot% Copy \fancyfoot into \oldfootrule
  - \renewcommand{\fancyfoot}{\color{bluerich}\oldfootrule}% Add colour to \fancyfoot
-->

```{r set-css, eval=FALSE, include=FALSE}
pacman::p_load(npm)
npm_install("chroma-sass", scope="dev")
pacman::p_load_gh("ehyaei/MPIThemes")
```


```{r eval=FALSE, include=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
 
# Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

# To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

#unlink("index_cache", recursive = TRUE) - is very usefl
#bookdown::serve_book()
#bookdown::render_book('index.Rmd', 'all')

```

<!-- Add anchors to # headings using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). 

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```
 
You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
 -->

```{r eval=FALSE, include=FALSE}
#at some point maybe explore these

library(officer)
library(magrittr)

doc_2 <- read_docx(path = "../report_draft.docx") %>% 
  body_add_par("Hello world!", style = "Normal") 

pptx_2 <- read_pptx(path = "../Attachments/evidence-base.pptx") 
doc_2 <- 
  
  body_add_docx


print(doc_2, target = "example_2.docx")

```
